### 2011-01-08 docs/slides/mimicry.tex
More slides added.
Some updates...

	\begin{itemize}
		\item Reduced predation lead.
		\item Contribution from naive young predators.
		\item Mutual advertising.
		\item Opportunity from mutation.
		\item Predator's generalization.
	\end{itemize}

	\begin{itemize}
		\item Mullerian mimicry is not deception.
		\item Predator's advantage to know all noxious species and deterrent species.
		\item Prey species creating the most traumatic stimuli to a predator have more possibility of the being the model.
	\end{itemize}
}

@@

	\begin{itemize}
		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
		\item Each cluster of species, all sharing a common pattern is termed as Mullerina mimicry ring.
		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.
	\end{itemize}	
}

>>>>

	\begin{itemize}
		\item Reduced predation load.
		\item Contribution from naive young predators.
		\item Mutual advertising.
		\item Opportunity from mutation.
		\item Predator's generalization.
	\end{itemize}

	\begin{itemize}
		\item Mullerian mimicry is not deception.
		\item Predator's advantage to know all noxious species and deterrent species.
		\item Prey creating most traumatic stimuli to a predator is the model.
	\end{itemize}
}

@@

	\begin{itemize}
		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
		\item Each cluster of species, all sharing a common pattern is termed as Mullerian mimicry ring.
		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.
	\end{itemize}	
}
